### 2018-10-03 paper/paper.tex
demand definiert

As the demand may vary over time, e.g.~in a seasonal pattern or simply by some variance, it must be
considered as time factor in formulation of the lead time syndrome. To clarify, consider a seasonal
demand. It can clearly not be considered a lead time syndrome if the releases just depict the
demand. However

>>>>

As the demand may vary over time, e.g.~in a seasonal pattern or simply by some variance, it must be
considered as time factor in the formulation of the lead time syndrome. To clarify, consider a
seasonal demand. It can clearly not be considered a lead time syndrome if the releases just depict
the demand.

Let the periodic demand be given by $\di{t}{t+1} = \dmean(\frac{t+t+1}{2}) + \epsilon$,
where $\dmean$ is a function which maps any given time $t \geqslant 0$ to the expected mean demand
at time $t$ and $\epsilon$ is drawn from a random variable $\X$ with standard deviation $\sigma$.

\begin{example}
  In case of a constant demand, $\dmean$ maps to a constant value, whereas in a seasonal demand $f$
  might be the sine-function. In most cases we expect the random variable to be drawn from the
  standard distribution: $\X \sim \N{0}{\sigma^{2}}$.
\end{example}

- je mehr variation im demand desto länger die zeit
